Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model \\ {\large \url{https://github.com/maxitg/GammaRays}}

### 2014-08-27 Paper/gammaRays.tex
Changed evclass to 2 in paper and in code

First, we use \texttt{gtselect}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtselect.txt}}.
We filter the Earth limb emission with it below the zenith angle of $100\degree$.

@@

Knowing the exposures, we can now use the method introduced in the appendix of \cite{Rubtsov:2011qq} to estimate the linear component of background from the data observed before the burst.
We compute two background estimates: for low and high energy bands.
Also, our method doesn't work for transient class photons, because their background appears to depend on the spacecraft position.
So we had to filter them out completely.

@@

The commands we use to invoke Fermi Science tools are the following:
\begin{lstlisting}
gtselect infile=[eventFile] outfile=filtered.fits
	ra=INDEF dec=INDEF rad=180 tmin=INDEF tmax=INDEF emin=100 emax=300000
	zmax=100 evclass=0 convtype=-1 evtable=EVENTS
\end{lstlisting}
Here \texttt{[eventFile]} is the file downloaded from the Fermi LAT data server.

>>>>

First, we use \texttt{gtselect}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtselect.txt}}.
We filter the Earth limb emission with it below the zenith angle of $100\degree$.
We also filter out photons with transient event class for a reason described in the next section.

@@

Knowing the exposures, we can now use the method introduced in the appendix of \cite{Rubtsov:2011qq} to estimate the linear component of background from the data observed before the burst.
We compute two background estimates: for low and high energy bands.
Finally, our method doesn't work for transient class photons, because their background appears to depend on the spacecraft position.
That is why we had to filter them out completely.

@@

The commands we use to invoke Fermi Science tools are the following:
\begin{lstlisting}
gtselect infile=[eventFile] outfile=filtered.fits
	ra=INDEF dec=INDEF rad=180 tmin=INDEF tmax=INDEF emin=100 emax=300000
	zmax=100 evclass=2 convtype=-1 evtable=EVENTS
\end{lstlisting}
Here \texttt{[eventFile]} is the file downloaded from the Fermi LAT data server.
